The Second Data Release of the INT Photometric H$\alpha$ Survey of the Northern Galactic Plane (IPHAS DR2)

### 2014-06-27 paper/iphas-dr2-arxiv.tex

\documentclass[a4paper,useAMS,usenatbib]{mn2e}
\usepackage{amssymb,amsmath}
\usepackage[pdftex]{graphicx}
\usepackage{longtable} 
\usepackage{float}
\usepackage{booktabs}
\usepackage{aas_macros}
\usepackage{caption}
\usepackage{subcaption}

@@

B. Mizalski$^{4}$,

@@

S. Pyrzas$^{26}$

@@

$^{14-32}$ (note to editor: affiliations 14 through 32 are given in the source file)

@@

The catalogue is made available through the
Vizier service (http://vizier.u-strasbg.fr),
where it can be queried using a web interface
and using Virtual Observatory (VO) protocols.
In addition, the catalogue can be downloaded
in its entirety from our website (www.iphas.org)
as a collection of binary FITS tables,
each covering a $5\degr\times5\degr$ tile
of the footprint and comprising 50~gigabyte
in total.

@@

To estimate absolute narrow-band \ha\ fluxes from the image data,
we note that the integrated in-band energy flux for Vega 
in the IPHAS \ha\ filter 
is $1.52 \times 10^{-7}$~erg\,cm$^{-2}$\,s$^{-1}$ 
at the top of the Earth's atmosphere,
which is the flux obtained by folding the 
CALSPEC SED with the filter transmission curve only
(the correction for atmosphere and detector quantum efficiency,
otherwise scales down the narrowband flux by 0.707).
This implies that the in-band flux corresponding to
zero magnitude is $1.56 \time 10^{-7}$ erg\,cm$^{-2}$\,s$^{-1}$,
when the \ha\ magnitude for Vega is set by convention to 0.03 \citep{Fukugita1996}.
These flux estimates are consistent with the most recent
version of Vega's SED presented by \citet{Bohlin2014}.

@@

\footnotesize{
  \bibliographystyle{mn2e}
  \bibliography{iphas-dr2}
}

>>>>

\documentclass[a4paper,useAMS,usenatbib]{mn2e}
\pdfpagewidth=\paperwidth
\pdfpageheight=\paperheight
\usepackage{amssymb,amsmath}
\usepackage[pdftex]{graphicx}
\usepackage{longtable} 
\usepackage{float}
\usepackage{booktabs}
\usepackage{aas_macros}
\usepackage{caption}
\usepackage{subcaption}

@@

B. Miszalski$^{4}$,

@@

S. Pyrzas$^{26}$,

@@

$^{14-32}$ (affiliations 14 through 32 are given in the source file)

@@

The catalogue will be made available through the
Vizier service (http://vizier.u-strasbg.fr),
where it can be queried using a web interface
and using Virtual Observatory (VO) protocols.
In addition, the catalogue can be downloaded
in its entirety from our website (www.iphas.org)
as a collection of binary FITS tables,
each covering a $5\degr\times5\degr$ tile
of the footprint and comprising 50~gigabyte
in total.

@@

To estimate absolute narrow-band \ha\ fluxes from the image data,
we note that the integrated in-band energy flux for Vega 
in the IPHAS \ha\ filter 
is $1.52 \times 10^{-7}$~erg\,cm$^{-2}$\,s$^{-1}$ 
at the top of the Earth's atmosphere,
which is the flux obtained by folding the 
CALSPEC SED with the filter transmission curve only
(the correction for atmosphere and detector quantum efficiency,
otherwise scales down the narrowband flux by 0.707).
This implies that the in-band flux corresponding to
zero magnitude is $1.56 \times 10^{-7}$ erg\,cm$^{-2}$\,s$^{-1}$,
when the \ha\ magnitude for Vega is set by convention to 0.03 \citep{Fukugita1996}.
These flux estimates are consistent with the most recent
version of Vega's SED presented by \citet{Bohlin2014}.

@@

\footnotesize{
  \bibliographystyle{mn2e}
  \bibliography{iphas-dr2-arxiv}
}
